A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-29 UAM2014/Article/article.tex
More on UAC2014

By coincidence our implementation is not so different from the SIGMAS+ simulator developed at the NATO Undersea Research Centre (NURC)~\cite{Coiras2009a, Coiras2009b}. They both take advantage of OpenGL to render a 2D image from 3D models, are designed for side-looking sonar, and assume a Lambertian scattering model. However, while SIGMAS+ is geared more towards realistically looking sonar images by including effects such as noise, we do not. Also, SIGMAS+ sum images obtained from multiple OpenGL rendering passes to create the sonar image, while we render once and tailor the sonar image with the flexibility of OpenCL.

@@

Before we can do anything with OpenGL we first have to set up the scene. This involves loading the models and then placing them where we want them with the proper orientation.

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Cylinder simulation with parameters adapted to fit the SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}%
\end{subfigure}
\caption{}
\end{figure}

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged.svg}%
\caption{``Typical'' parameters: Length 2.6\;m, burial depth 0.1\;m, aspect angle 100$^\circ$. }%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Parameters adapted to fit SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}%
\end{subfigure}
\caption{Cylinder simulations}\label{sim_cylinder}
\end{figure}

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged_bw.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_cylinder_bw}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged.svg}%
\caption{Cylinder simulation with ``typical'' parameters: Length 2.6\;m, burial depth 0.1\;m, aspect angle 100$^\circ$. }\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_bw.svg}%
\caption{Cylinder simulation with ``typical'' parameters: Length 2.6\;m, burial depth 0.1\;m, aspect angle 100$^\circ$.}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

\begin{figure}[tp]\centering%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Adaptive cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}\label{sim_cylinder}%
\end{subfigure}\hspace{\imgspacing}%
\begin{subfigure}[b]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive_bw.svg}%
\caption{Adaptive cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}\label{sim_cylinder_bw}%
\end{subfigure} 
\end{figure}

>>>>

By coincidence our implementation is not so different from the SIGMAS+ simulator developed at the NATO Undersea Research Centre (NURC)~\cite{Coiras2009a, Coiras2009b}. They both take advantage of OpenGL to render a 2D image from 3D models, are designed for side-looking sonar, and assume a Lambertian scattering model. However, while SIGMAS+ is geared more towards realistically looking sonar images, and include effects such as noise, we do not. Also, their simulator sums images obtained from multiple OpenGL rendering passes to create the sonar image, while we render once and post-process this result with OpenCL to tailor the sonar image full flexibility.

@@

Before we can render anything OpenGL we first have to set up the scene. This involves loading the models and then placing them where we want them with the proper orientation.

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Cylinder simulation with parameters adapted to fit the SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}%
\end{subfigure}
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure}

@@

@@
